Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-11 paper.tex
Suite intro

{\color{red} \begin{proposition} 
State here that the fixed points of   $\gamma^{l+1} =P^\theta_{\Ccal_2}(P^\theta_{\Ccal_1}(\gamma^l))$ are the same than $\gamma^{l+1} =P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l))$?
\end{proposition}}
\subsection{Lyapunov function}
Let $\gamma^*$ denote the solution of the regularized OT problem.
The function $F$ is defined as:
\begin{equation}\label{eq:lyapunov_function}
F(\gamma) = KL(\gamma^*, \gamma)
\end{equation}
It shall be used as a Lyapunov function, so that $F(\gamma^{k+1}) < F(\gamma^k)$ as long as the process has not converged.

@@

>>>>

{\color{blue} \begin{proposition} 
State here that the fixed points of   $\gamma^{l+1} =P^\theta_{\Ccal_2}(P^\theta_{\Ccal_1}(\gamma^l))$ are the same than $\gamma^{l+1} =P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l))$?
\end{proposition}}
\subsection{Lyapunov function}
Let $\gamma^*$ denote the solution of the regularized OT problem.
The function $F$ is defined as:
\begin{equation}\label{eq:lyapunov_function}
F(\gamma) = KL(\gamma^*, \gamma)
\end{equation}
It shall be used as a Lyapunov function, so that $F(\gamma^{k+1}) < F(\gamma^k)$ as long as the process has not converged.

@@

\section{Conclusion}

Cheaper test, how chosing $\omega$.

{\color{blue}
From experiments, it seems possible to design a good guess for $\omega$ from $c$ and $\epsilon$ only. For $K=e^{-c/\epsilon}$, let us  define:
    $T=(diag(K\mathbf{1}))^{-1}K(diag(K^T\mathbf{1}))^{-1}K^T$. The matrix $T$ is positive semidefinite and checks
$\rho(T)=1$. Moreover  $T$ has  only one  eigenvalue $1$ associated to the eigenvector $\mathbf{1}$.
    Denoting as $\lambda$ the second larger eigenvalue of $T$, one can set 
    $\omega=\frac{2}{\lambda}(1-\sqrt{1-\lambda})$.}
